---
title: "Official App"
author: "Maya Ziebarth"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Libraries 
```{r}
library(tidyverse)
library(janitor)
library(shiny)
library(shinydashboard)
library(ggmap)
library(ggplot2)
library(ggthemes)
library(shinythemes)
```


### Data
```{r}
clownfish_endurance <- read_csv("data/endurance_of_clownfish.csv") %>% clean_names()
long_lat <- read_csv("data/long_lat_fishes.csv") %>% clean_names()
```

### Graphs
```{r}
both_species <- long_lat %>% 
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Species") +
  theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
  theme_economist()+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(hjust = 0.5))
both_species
```

```{r}
clownfish <- long_lat %>% 
  filter(species=="Amphiprion percula") %>%
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Species") +
   theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
  theme_economist()+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(hjust = 0.5))
clownfish


cf <- long_lat %>% 
  filter(species=="Amphiprion percula")
```

``````{r}
bluetang <- long_lat %>% 
  filter(species=="Paracanthurus hepatus") %>%
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue")) +
  labs(title = "Distribution of Species") +
   theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
  theme_economist()+
  theme(legend.position = "bottom")+
  theme(plot.title = element_text(hjust = 0.5))
bluetang

bt <- long_lat %>% 
  filter(species=="Paracanthurus hepatus")
```



### Official Shiny App
```{r}
library(shiny)
library(shinydashboard)
library(shinythemes)
library(ggplot2)

ui <- dashboardPage(skin="yellow",
  dashboardHeader(title = "Summary App", titleWidth = 400),
  dashboardSidebar(disable = TRUE),
  dashboardBody(
titlePanel("Finding Nemo: How Far Did They Go?"),
    tabBox( width=2000, 
      title = "Pick Your Graph!",
      id = "tabs",
      tabPanel("Distrubution",
        box(
          title = "Options",
          width = 1000,
          height = 200,
          selectInput(
            "scatterplot_choice",
            "Select a Distribution",
            choices = c("Both Species", "Clown Fish", "Blue Tang"),
            selected = "Both Species"
              )
            ),
            box(
              width = 1000,
              height = 600,
              plotOutput("selected_scatterplot")
            )
      ),
      tabPanel("Clownfish Speed Distribution",
        box(
          width = 1000,
          height = 200,
          plotOutput("speed")
        )
      ),
      tabPanel("Clownfish Distance vs. Time",
        box(
          width = 1000,
          height = 200,
          plotOutput("dist_time")
 )
      ),
      tabPanel("Total Length of Clownfish",
        box(
          width = 1000,
          height = 200,
          plotOutput("tlength")
        )
      )
    )
 )
)


server <- function(input, output, session) {
 session$onSessionEnded(stopApp)
  selected_scatterplot <- reactive({
   switch(input$scatterplot_choice,
           "Both Species" = ggplot(long_lat, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
             labs(title = "Both Species")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5)),
           "Clown Fish" = ggplot(cf, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Amphiprion percula' = "orange")) +
             labs(title = "Clown Fish")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5)),
           "Blue Tang" = ggplot(bt, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Paracanthurus hepatus' = "blue")) +
             labs(title = "Blue Tang")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5))
    )
  })


  output$selected_scatterplot <- renderPlot({
    selected_scatterplot()
  })
  
    output$speed <- renderPlot({
    clownfish_endurance %>%
      ggplot(aes(speed)) +
      geom_histogram(bins = 5, color = "black", fill = "orange", alpha = 0.8) +
      labs(title = "Speed of Clownfish", x = "Speed (cm/sec)", y = "Frequency") +
      theme_economist() +
      theme(plot.title = element_text(hjust = 0.5))
  })
    
  output$dist_time <- renderPlot({
    clownfish_endurance %>%
  filter(dist_cm != "NA") %>%
  ggplot(aes(x= log10(dist_cm), y=log10(time_sec), color = speed)) +
  geom_point() +
  theme_economist() + 
  labs(title = "Clownfish Endurance", x = "log10 Distance (cm)", y = "log10 Time (sec)", color = "Speed (cm/sec)") + 
  theme(legend.position = "right") + 
  theme(plot.title = element_text(hjust = 0.5))
    
  })

  output$tlength <- renderPlot({
    clownfish_endurance %>%
    filter(tl != "NA") %>%
  ggplot(aes(tl)) + 
  geom_density(fill= "orange", alpha = 0.7) + 
  theme_economist() + 
  labs(title = "Total Length of Clownfish", x = "Total Length (cm)", y = "Density") + 
  theme(legend.position = "right") + 
  theme(plot.title = element_text(hjust = 0.5)) 
    
  })

  
}


shinyApp(ui, server)
```