---
title: "Brainstorm"
author: "Liana Williams"
date: "2024-02-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ideas

### idea 1 (APPROVED BY PROF!) ; HAS A RESEARCH ARTICLE ASSOCIATED
```{r}
#[Swimming Endurance Clown Fish](https://www.bco-dmo.org/dataset/739171) #inspired by Clownfish in Finding Nemo; not too long
```

### idea 2 (kinda boring ngl)
```{r}
#[Zooplankton Database](https://www.bco-dmo.org/dataset/526852) #good amount of quantitative vs. categorical data 
```


# Project Requirements  
Each group will prepare a short 5-7 minute presentation of their work. There should be a theme or "story" that can be shared, i.e. what were the big questions, challenges, and tools that you used? Did you learn an interesting new package or method that can be shared?

# Questions We're Asking
Is it feasible for a clownfish to travel such a distance to Sydney Australia? With the given amount of time?

What age would get there the fastest? 

# Structure


## Points to cover
1) Location where a clown fish (Amphiprion percula) and a blue tang (Paracanthurus hepatus) coexist around Australia 
1a) How far the location is from Sydney
2) Clown fish distance over time
3) Graphs of ages and distances 

App Idea: people can look at the maps of the differnt species and they can look at the ages v distances (basically summarizing out presentation)

## Tasks
*every person needs an assigned task*


### Liana - maps 
*longitude and latitude of clownfish and blue tang ; use colors from both*

*Frequency and association of Clownfish and Blue Tangs*


### Maya - app
*clean data*

*work with stella and combine data for app*

### Spencer - plots
*graphs for distance travelled of endurance data* 

*graphs for speed*

*graphs of speed versus time* 

*graph of overall fish length and size*


### Stella - app
*work with maya and combine data for app*

### Johnnie - plots
*graph the current and its velovity*

*Graph the distance of Marlin's journey*

*compare with spencers data about using the current to travel or not*

*Summarize the data to find the fastest Journey tiems*


# Cleaned CSV files we're using
endurance_of_clownfish.csv
long_lat_fishes.csv



