---
title: "Fish Data Johnnie"
author: "Johnnie Runyon"
date: "2024-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
#setwd("C:/Users/Johnn/Desktop/BIS_015L_Project/Indiv.Markdowns")
```

### Libraries
```{r}
#install.packages("luberdate")

#library(here)
#library(shinydashboard)
#library(shiny)
#library(luberdate)
#library("tidyverse")
#library("janitor")
#library(RColorBrewer)
#library(paletteer)
```


After his son is captured in the Great Barrier Reef and taken to Sydney, a timid clownfish sets out on a journey to bring him home.

Nemo and Marlin live near the Great Barrier Reef. This is where Nemo was taken.

Marlin pursues the boat

His journey: 

1) bumps into Dory, a blue tang with acute short-term memory loss, who offers her help

2) The two encounter Bruce, Anchor, and Chum, three sharks who have sworn to abstain from eating fish. Marlin finds a diver's mask that fell from the boat, accidentally hitting Dory. The scent of her blood sends Bruce into a frenzy and he accidentally sets off old naval mines that knock Marlin and Dory unconscious.

3) Marlin and Dory wake up but the mask falls into a deep trench. Swimming after it, they are attacked by an anglerfish.

4) Dory memorizes the address on the goggles before they escape. The two take directions for East Australian Current from a school of moonfish but find themselves in a forest of jellyfish.

5) Stung and knocked unconscious, they awaken in the East Australian Current with a large group of sea turtles, including Crush and his son, Squirt.

6) The sea turtles take Marlin and Dory to their Sydney exit, where they get lost and are consumed by a blue whale.

7) The whale expels them through its blowhole into Sydney Harbour.

8) A pelican named Nigel takes them to Sherman's office

## Questions

Can a clounfish and a blue tang swim all the way from the great barrier reef to sydney?
Where is sydney?
How far is sydney from the great barrier reef?
What is the endurance of a clownfish?
How fast can a clownfish swim?
What type of clownfish?
How soon do the fish need to reach nemo?
Where do clownfish and blue tangs coexist?

Age
species
gender

how would clownfish and blue tangs coexist
how likely are these fish to survive an encounter with those sharks?
what type of sharks?
how likely are these fish to survive an angler fish?
type of anglerfish?
survival with jellyfish?
where is the East Australian Current and how fast does it go?
location of the current exit and sydney harbor
blue whale speed


1) Location where a clown fish (Amphiprion percula) and a blue tang (Paracanthurus hepatus) coexist around Australia 
1a) How far the location if from Sydney
2) Clown fish distance over time
3) Graphs if ages and distances 



























