---
title: "Fish Data Maya"
author: "Maya"
date: "2024-02-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(naniar)
library(skimr)
library(shiny)
library(shinydashboard)
```

### Data clean up

#### Endurance data
```{r}
endurance <- read_csv("data/endurance.csv") %>% clean_names()
```

to do:
 1) filter out all except Amphiprion percula
 2) rename "nd" to "0", it means no distance so that is equal to 0
 3) take out location, its all at Boston University Lab and unimportant to be repeated 

```{r}
endurance_clownfish <- endurance %>% 
  filter(species=="Amphiprion percula") %>% 
  select(-"location") %>% 
  replace_with_na(replace = list(tl = "nd",
                                 sl = "nd",
                                 bd = "nd",
                                 pa = "nd",
                                 time_sec = "nd",
                                 dist_cm = "nd",
                                 speed = "nd"))
```
 
#### Location data
```{r}
pointmap <- read_csv("data/fishes_pointmap.csv") %>% clean_names()
```

to do: 
 1) remove NAs
 2) filter out unnecessary 
 3) rename "names_used" to "species"
 
```{r}
pointmap_fishes <- pointmap %>% 
  filter(name_used=="Paracanthurus hepatus" | name_used=="Amphiprion percula") %>% 
  select(name_used, year, latitude, longitude) %>% 
  rename(species="name_used")
```


```{r}
write.csv(endurance_clownfish, "endurance_of_clownfish.csv", row.names = FALSE)
```

```{r}
write.csv(pointmap_fishes, "long_lat_fishes.csv", row.names = FALSE)
```


### Loading in data
load in the lat_log_fishes.csv and endurance_of_clownfish.csv
```{r}
clownfish_endurance <- read_csv("data/endurance_of_clownfish.csv") %>% clean_names()
long_lat <- read_csv("data/long_lat_fishes.csv") %>% clean_names()
```

summarize 
```{r}
long_lat %>% 
  group_by(species) %>% 
  summarize(max_lat=max(latitude), min_lat=min(latitude), max_long=max(longitude), min_long=min(longitude))
```

All the libraries 
```{r}
library(ggplot2)
library(ggmap)
library(shiny)
library(shinydashboard)
library(shinythemes)
library(ggthemes)
```

## lianas maps with my api key
```{r}
register_stadiamaps("API", write = FALSE)
```

    ### Clownfish distrubution map
```{r}
# Filter df for the species 'Amphiprion percula' in Australia
long_lat_australia <- long_lat[long_lat$species == 'Amphiprion percula',]

# Define the bounding box for Australia
lat_range <- c(-43.00311, -10.062805)  # Australia's approximate latitudinal range
long_range <- c(113.6594, 153.61194)   # Australia's approximate longitudinal range
bbox_australia <- c(left = min(long_range), bottom = min(lat_range), right = max(long_range), top = max(lat_range))

# Get the base map for the bounding box area
map_australia <- get_stadiamap(bbox = bbox_australia, maptype = "stamen_terrain", zoom = 6)

# Plot the base map with points from long_lat_australia
ggmap(map_australia) +
  geom_point(data = long_lat_australia, aes(x = longitude, y = latitude, color = species), size = 1.5) +
  scale_color_manual(values = c('Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Amphiprion percula in Australia", 
       x="Longitude",
       y="Latitude") +
  theme(legend.position = "bottom")
```
    ### Blue tang distribution map
```{r}
library(ggplot2)
library(ggmap)

# Filter df for the species 'Paracanthurus hepatus'
long_lat_paracanthurus <- long_lat[long_lat$species == 'Paracanthurus hepatus',]

# Define the bounding box based on the min and max ranges of longitude and latitude for 'Paracanthurus hepatus'

lat_range_paracanthurus <- range(long_lat_paracanthurus$latitude)
long_range_paracanthurus <- range(long_lat_paracanthurus$longitude)
bbox_paracanthurus <- c(left = min(long_range_paracanthurus), bottom = min(lat_range_paracanthurus), 
                       right = max(long_range_paracanthurus), top = max(lat_range_paracanthurus))

# Get the base map for the bounding box area
map_paracanthurus <- get_stadiamap(bbox = bbox_paracanthurus, maptype = "stamen_terrain", zoom = 4)

# Plot the base map with points from df_paracanthurus
ggmap(map_paracanthurus) +
  geom_point(data = long_lat_paracanthurus, aes(x = longitude, y = latitude), color = "blue", size = 1) +
  labs(title = "Distribution of Paracanthurus hepatus", 
       x="Longitude",
       y="Latitude") +
  theme(legend.position = "bottom")
```


    ### map of both species
```{r}
library(ggplot2)
library(ggmap)

# Define the bounding box based on the min and max ranges of longitude and latitude for both species
lat_range <- range(long_lat$latitude)
long_range <- range(long_lat$longitude)
bbox_species <- c(left = min(long_range), bottom = min(lat_range), 
                  right = max(long_range), top = max(lat_range))

# Get the base map for the bounding box area
map_species <- get_stadiamap(bbox = bbox_species, maptype = "stamen_terrain", zoom = 3)

# Plot the base map with points from df for both species
ggmap(map_species) +
  geom_point(data = long_lat, aes(x = longitude, y = latitude, color = species), size = 1, alpha=0.7) +
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Both Species", 
       x="Longitude",
       y="Latitude") +
  theme(legend.position = "bottom")
```


### Graphs I made for the shiny app
```{r}
both_species <- long_lat %>% 
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Species") +
  theme(legend.position = "bottom")
both_species
```

```{r}
clownfish <- long_lat %>% 
  filter(species=="Amphiprion percula") %>%
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Species") +
  theme(legend.position = "bottom")
clownfish
```

```{r}
cf <- long_lat %>% 
  filter(species=="Amphiprion percula")
```



```{r}
bluetang <- long_lat %>% 
  filter(species=="Paracanthurus hepatus") %>%
  ggplot(aes(x=longitude, y= latitude, color=species))+
  geom_point(size = 1, alpha=0.7)+
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue")) +
  labs(title = "Distribution of Species") +
  theme(legend.position = "bottom")
bluetang
```

```{r}
bt <- long_lat %>% 
  filter(species=="Paracanthurus hepatus")
```


### Shiny App
```{r}
library(shiny)
library(shinydashboard)
library(shinythemes)
library(ggplot2)

ui <- dashboardPage(skin="yellow",
  dashboardHeader(title = "Summary App", titleWidth = 400),
  dashboardSidebar(disable = TRUE),
  dashboardBody(
titlePanel("Finding Nemo: How Far Did They Go?"),
    tabBox( width=2000, 
      title = "Pick Your Graph!",
      id = "tabs",
      tabPanel("Distrubution",
        box(
          title = "Options",
          width = 1000,
          height = 200,
          selectInput(
            "scatterplot_choice",
            "Select a Distribution",
            choices = c("Both Species", "Clown Fish", "Blue Tang"),
            selected = "Both Species"
              )
            ),
            box(
              width = 1000,
              height = 600,
              plotOutput("selected_scatterplot")
            )
      ),
      tabPanel("Clownfish Speed Distribution",
        box(
          width = 1000,
          height = 200,
          plotOutput("speed")
        )
      ),
      tabPanel("Clownfish Distance vs. Time",
        box(
          width = 1000,
          height = 200,
          plotOutput("dist_time")
 )
      ),
      tabPanel("Total Length of Clownfish",
        box(
          width = 1000,
          height = 200,
          plotOutput("tlength")
        )
        ),
        tabPanel("Time to Sydney with Current",
        box(
          width = 1000,
          height = 200,
          plotOutput("timecurrent")
        )
        )
      )
    )
 )


server <- function(input, output, session) {
 session$onSessionEnded(stopApp)
  selected_scatterplot <- reactive({
   switch(input$scatterplot_choice,
           "Both Species" = ggplot(long_lat, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
             labs(title = "Both Species")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5)),
           "Clown Fish" = ggplot(cf, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Amphiprion percula' = "orange")) +
             labs(title = "Clown Fish")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5)),
           "Blue Tang" = ggplot(bt, aes(x = longitude, y = latitude, color = species)) +
             geom_point(size = 3, alpha = 0.7) +
             scale_color_manual(values = c('Paracanthurus hepatus' = "blue")) +
             labs(title = "Blue Tang")+
            theme(plot.title=element_text(size=rel(1.75), hjust = 0.5))+
            theme_economist()+
            theme(legend.position = "bottom") + 
  theme(plot.title = element_text(hjust = 0.5))
    )
  })


  output$selected_scatterplot <- renderPlot({
    selected_scatterplot()
  })
  
    output$speed <- renderPlot({
    clownfish_endurance %>%
      ggplot(aes(speed)) +
      geom_histogram(bins = 5, color = "black", fill = "orange", alpha = 0.8) +
      labs(title = "Speed of Clownfish", x = "Speed (cm/sec)", y = "Frequency") +
      theme_economist() +
      theme(plot.title = element_text(hjust = 0.5))
  })
    
  output$dist_time <- renderPlot({
    clownfish_endurance %>%
  filter(dist_cm != "NA") %>%
  ggplot(aes(x= log10(dist_cm), y=log10(time_sec), color = speed)) +
  geom_point() +
  theme_economist() + 
  labs(title = "Clownfish Endurance", x = "log10 Distance (cm)", y = "log10 Time (sec)", color = "Speed (cm/sec)") + 
  theme(legend.position = "right") + 
  theme(plot.title = element_text(hjust = 0.5))
    
  })

  output$tlength <- renderPlot({
    clownfish_endurance %>%
    filter(tl != "NA") %>%
  ggplot(aes(tl)) + 
  geom_density(fill= "orange", alpha = 0.7) + 
  theme_economist() + 
  labs(title = "Total Length of Clownfish", x = "Total Length (cm)", y = "Density") + 
  theme(legend.position = "right") + 
  theme(plot.title = element_text(hjust = 0.5)) 
    
  })

  output$timecurrent <-renderPlot ({
    clownfish_endurance_2 %>% 
  select(dist_km, time_hr) %>%
  mutate(speed_with_current = dist_km/time_hr + 7) %>% 
  mutate(days_to_sydney = (1860 / speed_with_current) / 24)  %>%
  ggplot(aes(days_to_sydney)) + 
  geom_density(fill = "orange", alpha = 0.7) +
  theme_economist() +
  labs(title = "Time to Sydney with the Current", x = "Time (Days)", y = "Density") + 
  theme(plot.title = element_text(hjust = 0.5))
    })
}


shinyApp(ui, server)
```


