---
title: "Fish Data Spencer"
author: "Spencer"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
    
    
## Load packages. 
    
```{r}
library(tidyverse)
library(janitor)
library(dplyr)
library(skimr)
library(ggthemes)
```
    
    
## Turn off scientific notation. 
    
```{r}
options(scipen = 999)
```


## Input fish data, names are already clean. 
    
```{r}
clownfish_endurance <- read_csv("data/endurance_of_clownfish.csv")
```
  
  
## Distribution of speeds of clownfish larvae. 
    
```{r} 
clownfish_endurance %>%
  ggplot(aes(speed)) +
  geom_histogram(bins = 5, color= "black", fill = "orange", alpha = 0.8) + 
  labs(title = "Speed of Clownfish", x = "Speed (cm/sec)", y = "Frequency") + 
  theme_economist() + 
  theme(plot.title = element_text(hjust = 0.5))
  
```
  
    
## Scatter plot for distance travelled over time.  
    
```{r} 
# move graph legend to the left, title to the middle


clownfish_endurance %>%
  filter(dist_cm != "NA") %>%
  ggplot(aes(x= log10(dist_cm), y=log10(time_sec), color = speed)) +
  geom_point() +
  theme_economist() + 
  labs(title = "Clownfish Endurance", x = "Distance ( log10(cm) )", y = "Time ( log10(sec) )", color = "Speed (cm/sec)") + 
  theme(legend.position = "right") + 
  theme(plot.title = element_text(hjust = 0.5))
```
 
 
## Clownfish data into kilometers and hours. 
    
```{r}
clownfish_endurance_2 <- clownfish_endurance %>%
  filter(dist_cm != "NA") %>%
  select(speed, dist_cm, time_sec) %>%
  mutate(dist_km = dist_cm / 100000) %>%
  mutate(time_hr = time_sec / 3600) %>%
  arrange(-dist_km)
```


## Speed in kilometers/ hour. 
    
```{r}
clownfish_endurance_2 %>%
  select(dist_km, time_hr) %>%
  mutate(speed_km_hr = dist_km / time_hr) %>%
  top_n(10, dist_km) %>%
  arrange(-dist_km)
```
    
    
## Time it takes to travel to Sydney with mutated speed variabel to factor in speed of East Australian current (+7km/hr). 
    
    TABLE. 
    
```{r}
clownfish_endurance_2 %>% 
  select(dist_km, time_hr) %>%
  mutate(speed_with_current = dist_km/time_hr + 7) %>% 
  mutate(days_to_sydney = (1860 / speed_with_current) / 24)  %>%
  arrange(-dist_km)
```
    
    GRAPH. 
    
```{r}
clownfish_endurance_2 %>% 
  select(dist_km, time_hr) %>%
  mutate(speed_with_current = dist_km/time_hr + 7) %>% 
  mutate(days_to_sydney = (1860 / speed_with_current) / 24)  %>%
  ggplot(aes(days_to_sydney)) + 
  geom_density(fill = "orange", alpha = 0.7) +
  theme_economist() +
  labs(title = "Time to Sydney with Current", x = "Time (Days)", y = "Density") + 
  theme(plot.title = element_text(hjust = 0.5))
```


## Total length of clownfish distribution. 
    
```{r}
clownfish_endurance %>%
    filter(tl != "NA") %>%
  ggplot(aes(tl)) + 
  geom_density(fill= "orange", alpha = 0.7) + 
  theme_economist() + 
  labs(title = "Total Length of Clownfish", x = "Total Length (cm)", y = "Density") +
  theme(plot.title = element_text(hjust = 0.5))
```

