---
title: "Maps"
author: "Liana Williams"
date: "2024-03-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load the Libraries 
```{r}
library(tidyverse)
library(janitor)
library(skimr)
library(naniar)
library(visdat)
library(RColorBrewer)
library(paletteer)
#install.packages("ggmap")
library(ggmap)
```
**Liana - maps**

Load the data for longitude and latitude of clownfish and blue tang
```{r}
long_lat <- read_csv("data/long_lat_fishes.csv") %>% clean_names()
```

#Scatterplot of the longitude and latitude of clownfish and blue tang
```{r}
#Make a scatterplot of the clownfish and blue tang
long_lat %>%
  ggplot(aes(x = longitude, y = latitude, color = species)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("orange", "blue")) + #make the colors the same as Marlin and Dory so, the colors are consistent. 
  labs(title = "Longitude and Latitude of Clownfish and Blue Tang")
```

**Our goal here is to plot the Amphirion Percula (clownfish) and Paracanthurus hepatus (blue tang) locations from the columns which contain the latitude and longitude.**

Load a map from `stamen` in a terrain style projection and display the map. 
```{r}
register_stadiamaps("ae9b303b-2453-44b9-8f34-55a7a872cf5c", write = FALSE)
```

#Map the longitude and latitude of Amphiprion percula in Australia
```{r}
library(ggplot2)
library(ggmap)

# Filter df for the species 'Amphiprion percula' in Australia
long_lat_australia <- long_lat[long_lat$species == 'Amphiprion percula',]

# Define the bounding box for Australia
lat_range <- c(-43.00311, -10.062805)  # Australia's approximate latitudinal range
long_range <- c(113.6594, 153.61194)   # Australia's approximate longitudinal range
bbox_australia <- c(left = min(long_range), bottom = min(lat_range), right = max(long_range), top = max(lat_range))

# Get the base map for the bounding box area
map_australia <- get_stadiamap(bbox = bbox_australia, maptype = "stamen_terrain", zoom = 6)

# Plot the base map with points from long_lat_australia
ggmap(map_australia) +
  geom_point(data = long_lat_australia, aes(x = longitude, y = latitude, color = species), size = 1.5) +
  scale_color_manual(values = c('Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Amphiprion percula in Australia") +
  theme(legend.position = "none")
```

#Map the longitude and latitude of Paracanthurus hepatus
```{r}
library(ggplot2)
library(ggmap)

# Filter df for the species 'Paracanthurus hepatus'
long_lat_paracanthurus <- long_lat[long_lat$species == 'Paracanthurus hepatus',]

# Define the bounding box based on the min and max ranges of longitude and latitude for 'Paracanthurus hepatus'

lat_range_paracanthurus <- range(long_lat_paracanthurus$latitude)
long_range_paracanthurus <- range(long_lat_paracanthurus$longitude)
bbox_paracanthurus <- c(left = min(long_range_paracanthurus), bottom = min(lat_range_paracanthurus), 
                       right = max(long_range_paracanthurus), top = max(lat_range_paracanthurus))

# Get the base map for the bounding box area
map_paracanthurus <- get_stadiamap(bbox = bbox_paracanthurus, maptype = "stamen_terrain", zoom = 6)

# Plot the base map with points from df_paracanthurus
ggmap(map_paracanthurus) +
  geom_point(data = long_lat_paracanthurus, aes(x = longitude, y = latitude), color = "blue", size = 1) +
  labs(title = "Distribution of Paracanthurus hepatus") +
  theme(legend.position = "none")
```

#Map that plots both species longitude and latitude and color codes them
```{r}
library(ggplot2)
library(ggmap)

# Define the bounding box based on the min and max ranges of longitude and latitude for both species
lat_range <- range(long_lat$latitude)
long_range <- range(long_lat$longitude)
bbox_species <- c(left = min(long_range), bottom = min(lat_range), 
                  right = max(long_range), top = max(lat_range))

# Get the base map for the bounding box area
map_species <- get_stadiamap(bbox = bbox_species, maptype = "stamen_terrain", zoom = 4)

# Plot the base map with points from df for both species
ggmap(map_species) +
  geom_point(data = long_lat, aes(x = longitude, y = latitude, color = species), size = 1, alpha=0.7) +
  scale_color_manual(values = c('Paracanthurus hepatus' = "blue", 'Amphiprion percula' = "orange")) +
  labs(title = "Distribution of Species") +
  theme(legend.position = "bottom")
```